\documentclass[a4paper, 11pt]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage{cite}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue]{hyperref}

\begin{document}
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{\alph{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}

\section{Domain Description}

\textbf{Food Chain}
\vspace{3mm}

\noindent
In the food chain, there exist several species. Each species has an ID, one or more common names, a scientific name and a diet. \\ \\
These species all live in an ecosystem. 
Ecosystems consist of a name, location and area code as well as a climate and area in km.
Each ecosystem will also have a keystone species, that is, a species that has the greatest effect on an ecosystem \cite{paine_note_1969}.
There can only be one keystone species in an ecosystem and a species can only be keystone in one ecosystem. \\ \\
Researchers are assigned to study the species.
One researcher can study a variety of species and there is no need for more than one researcher studying a species at any one time.
Researchers will have a name, area of expertise and an ORCID ID.\\ \\
Each researcher will supervise a number of students.
Keep track of the students names, courses and year of study. \\ \\
The species in an ecosystem can interact with each other. This interaction type also needs to be recorded (Predation, parisitism, symbiosis etc).


\subsection{Entities}

\begin{itemize}
    \item Species
    \item Ecosystem
    \item Researcher
    \item Student (weak)
\end{itemize}

\subsection{1:1 Binary relationships}

\begin{itemize}
    \item Keystone Species $\leftrightarrow$ Ecosystem
\end{itemize}

\subsection{1:N Binary relationships}

\begin{itemize}
    \item Researcher $\leftrightarrow$ Species
    \item Researcher $\leftrightarrow$ Students
\end{itemize}

\subsection{M:N Binary relationships}

\begin{itemize}
    \item Species $\leftrightarrow$ Ecosystem
\end{itemize}

\subsection{Recursive relationships}

\begin{itemize}
    \item Species $\leftrightarrow$ Species (Interactions)
\end{itemize}

\subsection{Weak entities or multivalued composite attributes}

\begin{itemize}
    \item Species common name (Comp/Multi)
    \item Student (Weak Entity)
\end{itemize}

\bibliographystyle{plain}
\bibliography{domain}

\end{document}